Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-19 snapshot_system/fast14_deduplication.tex

Since each file block (with default size $64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.  From the above equations:
\[
\frac{N_1}{N_o}=  \frac{1-\sigma}{V_o}<1.
\] 
Thus when there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a lower chance to lose a snapshot than the VO approach because
$N_1<N_o$. 
Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
our test dataset.
%which shows how many VMs the failure of a single block can affect. 
For VC, we only show
the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
one VM.
%We can also observe that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
%This is likely because the PDS FSBs tightly pack data used by many VMs, 
%which decreases the overall number of FSBs required to backup a VM.
%If  the backup for multiple VMs is conducted concurrently, there would be more
%VMs shared  by each file block on average. Therefore,
%even when there is a loss of a PDS block, the VC approach tolerates the fault better.

@@

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
                width=\linewidth,
                height=0.6\linewidth,
		xlabel={Number of VMs},
		ylabel={Avg. Num. FSBs used by VM},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=south west
		]
                \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
                \legend{$N_o$, $N_1+N_2$, $N_1$, $N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}

@@

\item
When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
\[
(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
*
(1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
\]
Figure~\ref{fig:fsb-availability} illustrates that the availability of an individual file system block
with different replication degree. This demonstrates inequality $1-\frac{ \binom{d}{r}} { \binom{p}{r} }
< 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$. As we have also observed
$N_1+N_2 <N_o$ in our dataset, these two conditions support that VC has a  higher availability. 
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
\end{itemize}

\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={Availability of Single FSB (\%)},
            extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of individual file system blocks in a 100 machine cluster with different replication degrees.}
  \label{fig:fsb-availability}
\end{figure}

>>>>

Since each file block (with default size $64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.  From the above equations:
\[
\frac{N_1}{N_o}=  \frac{1-\sigma}{V_o}<1.
\] 
Thus when there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a lower chance to lose a snapshot than the VO approach because
$N_1<N_o$. 
Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
our test dataset.
%which shows how many VMs the failure of a single block can affect. 
For VC, we only show
the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
one VM.
From data, 
we have observed that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
This is likely because the PDS FSBs tightly pack data used by many VMs, 
which decreases the overall number of FSBs required to backup a VM.
Also if  the backup for multiple VMs were conducted concurrently, there would be more
VMs shared  by each file block on average in VO. 
%Therefore, even when there is a loss of a PDS block, the VC approach tolerates the fault better.

@@

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
                width=\linewidth,
                height=0.6\linewidth,
		xlabel={Number of VMs},
		ylabel={Avg. Num. FSBs used by VM},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=south west
		]
                \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
                \legend{$N_o$, $N_1+N_2$, $N_1$, $N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}

@@

\item
When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
\[
(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
*
(1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
\]
Figure~\ref{fig:fsb-availability} illustrates that the availability of an individual file system block
with different replication degree. This demonstrates inequality $1-\frac{ \binom{d}{r}} { \binom{p}{r} }
< 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$.  Since $N_1$ is much smaller than $N_o$ as discussed previously, 
these two conditions support that VC has a  higher availability. 
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
\end{itemize}

\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={Availability of Single FSB (\%)},
            extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of a file system block in a 100 machine cluster with different replication 
and failure settings.}
  \label{fig:fsb-availability}
\end{figure}
